RNA-seq from 4 cell populations

### 2021-08-02 deconvolution/fans4/molec_profiling.Rmd
bug fix

# TODO 
replace with FilterExpr()

@@

```{r preprocess}
isexpr = rowSums(edgeR::cpm(geneCounts)>1) >= 0.1*ncol(geneCounts)
table(isexpr)

@@

## Plots of top differentially expressed genes
```{r DE.marker_genes, fig.width=15, fig.height=30}

@@

  isexpr = rowSums(edgeR::cpm(geneCounts[,idx])>1) >= 0.3*ncol(geneCounts[,idx])
  table(isexpr)
  infoSub = droplevels(info[idx,])

@@

```{r CV.all.in.one, eval=TRUE}
library(scran)
# FANS4
isexpr = rowSums(edgeR::cpm(geneCounts)>1) >= 0.3*ncol(geneCounts)

@@

isexpr = rowSums(edgeR::cpm(gtex_count[,idx])>1) >= 0.3*ncol(gtex_count[,idx])

@@

  isexpr = rowSums(edgeR::cpm(geneCounts[,id])>1) >= 0.1*ncol(geneCounts[,id])

@@

  isexpr = rowSums(edgeR::cpm(gtex_count[,id])>1) >= 0.1*ncol(gtex_count[,id])

@@

isexpr = rowSums(edgeR::cpm(countsCombined)>1) >= 0.3*ncol(countsCombined)

@@

    isexpr = rowSums(edgeR::cpm(geneCountSub[,idx])>1) >= 0.3*ncol(geneCountSub[,idx])
    table(isexpr)

@@

fitDisease = dream( vobj[1:10,], form, info, L=L, BPPARAM=SnowParam(12, progressbar=TRUE))
```

>>>>

# TODO 
replace with FilterExpr()
add single cell
Add CMC bulk RNA-seq

@@

```{r preprocess}
# isexpr = rowSums(edgeR::cpm(geneCounts)>1) >= 0.1*ncol(geneCounts)
isexpr = filterByExpr(geneCounts, model.matrix(~CellType, info))
table(isexpr)

@@

## Plots of top differentially expressed genes
```{r DE.marker_genes, fig.width=15, fig.height=40}

@@

  # isexpr = rowSums(edgeR::cpm(geneCounts[,idx])>1) >= 0.3*ncol(geneCounts[,idx])
  isexpr = filterByExpr(geneCounts[,idx], model.matrix(~CellType, info[idx,]))
  table(isexpr)
  infoSub = droplevels(info[idx,])

@@

```{r CV.all.in.one, eval=TRUE}
library(scran)
# FANS4
# isexpr = rowSums(edgeR::cpm(geneCounts)>1) >= 0.3*ncol(geneCounts)
isexpr = filterByExpr(geneCounts, model.matrix(~CellType, info))

@@

# isexpr = rowSums(edgeR::cpm(gtex_count[,idx])>1) >= 0.3*ncol(gtex_count[,idx])
isexpr = filterByExpr(geneCounts[,idx], model.matrix(~CellType, info[idx,]))

@@

  # isexpr = rowSums(edgeR::cpm(geneCounts[,id])>1) >= 0.1*ncol(geneCounts[,id])
  isexpr = filterByExpr(geneCounts[,id], model.matrix(~CellType, info[id,]))

@@

  # isexpr = rowSums(edgeR::cpm(gtex_count[,id])>1) >= 0.1*ncol(gtex_count[,id])
  isexpr = filterByExpr(geneCounts[,id], model.matrix(~CellType, info[id,]))

@@

# isexpr = rowSums(edgeR::cpm(countsCombined)>1) >= 0.3*ncol(countsCombined)
isexpr = filterByExpr(countsCombined, model.matrix(~CellType, countsCombined))

@@

    # isexpr = rowSums(edgeR::cpm(geneCountSub[,idx])>1) >= 0.3*ncol(geneCountSub[,idx])
    isexpr = filterByExpr(geneCountSub[,idx], model.matrix(~CellType, info[idx,]))
    table(isexpr)

@@

fitDisease = dream( vobj, form, info, L=L, BPPARAM=SnowParam(12, progressbar=TRUE))
```
